---
title: "Title Goes Here"
author:
  - Juan Henao:
      correspondence: "yes"
title-block-published: "PIPE: Static vs Dynamic"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---


Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`


```{r}
library(DESeq2)
library(ggplot2)
library(ggrepel)
library(gprofiler2)
library(openxlsx)
library(dplyr)

set_base_url("https://biit.cs.ut.ee/gprofiler_archive3/e104_eg51_p15")

volcano_plot <- function(exp, down_color, up_color, title, subtitle){
  colnames(exp)[grep(pattern = "log2FoldChange",x = colnames(exp))] <- "log2FoldChange"
  colnames(exp)[grep(pattern = "padj",x = colnames(exp))] <- "padj"
  
  exp$direction <- "No-significant"
  
  exp$direction[which(exp$padj < 0.05 & exp$log2FoldChange > 0)] <- "Up-regulated"
  exp$direction[which(exp$padj < 0.05 & exp$log2FoldChange < 0)] <- "Down-regulated"
  
  exp <- exp[order(exp$padj),]
  
  exp$threshold <- c(rep(TRUE,10),rep(FALSE,nrow(exp) - 10))
  exp$direction <- as.factor(exp$direction)
  result <- exp[which(!is.na(exp$padj)),]
  result <- result[order(result$threshold,decreasing = TRUE),]
  
  ggplot(result) +
    geom_point(aes(x=log2FoldChange, y=-log10(padj),colour=direction)) + 
    scale_color_manual(values=c(down_color,"grey",up_color)) + labs(title=title,  subtitle=subtitle) +
    geom_text_repel(data =result[c(1:10),], 
                    mapping =aes(x= log2FoldChange, y = -log10(padj), label = result$name[c(1:10)] ), size = 2.5) +
    xlab("log2 fold change") + 
    ylab("-log10 adj. p-value") +
    geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "black") + theme_classic() + theme(legend.position = "none", 
                                                                                                    text = element_text(size = 8),
                                                                                                    plot.title = element_text(size=8)) 
  
}
loc_val <- function(mean_FC,SD){
  result <- c()
  for(i in seq(length(mean_FC))){
    if(SD[i] == 0){SD[i] <- min(SD[which(SD != 0)])}
    
    if(mean_FC[i] < 0){
      result <- c(result,mean_FC[i]-SD[i]-(min(SD[i])/2))
    }
    if(mean_FC[i] > 0){
      result <- c(result,mean_FC[i]+SD[i]+(min(SD[i])/2))
    }
    if(mean_FC[i] == 0){
      result <- c(result,NA)
    }
  }
  return(result)
}
enrichment_profile = function(pathways, DEG, color_down, color_up,title,subtitle){
  # data is the dataframe containing only significant genes for a specific cell type
  # pathway is a df of pathway ids/go ids that are statistically enriched from geneprofile
  
  DEG$name <- rownames(DEG)
  
  colnames(DEG)[grep(pattern = "log2fc",x = colnames(DEG))] <- "log2FoldChange"
  colnames(DEG)[grep(pattern = "pvalue",x = colnames(DEG))] <- "padj"
  colnames(DEG)[grep(pattern = "name",x = colnames(DEG))] <- "ensembl_gene_id"
  
  to.plot <- data.frame()
  for(i in 1:nrow(pathways)){
    res = gost(query = pathways[i,"term_id"], organism = "hsapiens")
    gene_set = res$meta$genes_metadata$query$query_1$ensgs
    
    to.plot <- rbind(to.plot,
                     data.frame(
                       Name=pathways[i,"term_name"],
                       mean_FC=c(mean(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange > 0]),
                                 mean(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange < 0])),
                       Type=c("up-regulated","down-regulated"),
                       Set_size = c(length(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange > 0]),
                                    length(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange < 0])),
                       SD=c(sd(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange > 0]),
                            sd(DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange[DEG[DEG$ensembl_gene_id %in% gene_set,]$log2FoldChange < 0]))
                     ))
  }
  
  to.plot[is.nan(to.plot$mean_FC),"mean_FC"] <- 0
  to.plot[is.na(to.plot$SD),"SD"] <- 0
  
  to.plot$Name[which(to.plot$Name == "Regulation of Insulin-like Growth Factor (IGF) transport and uptake by Insulin-like Growth Factor Binding Proteins (IGFBPs)")] <- "Regulation of Insulin-like Growth Factor\n (IGF) transport and uptake by Insulin-like\n Growth Factor Binding Proteins (IGFBPs)"
  
  to.plot$Name[which(to.plot$Name == "Assembly of collagen fibrils and other multimeric structures")] <- "Assembly of collagen fibrils\n and other multimeric structures"
  
  
  p <- ggplot(to.plot, aes(x = mean_FC, y = reorder(Name, abs(mean_FC)), fill = Type, label = Set_size)) + 
    scale_fill_manual(name = "", values = c("down-regulated" = color_down, "up-regulated" = color_up)) + 
    xlab("Mean logFC") + ylab("") +
    labs(title=title, subtitle=subtitle) +
    theme(axis.line = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank()) + theme(text = element_text(size = 8), plot.title = element_text(size=8)) + 
    theme(legend.position = "none") +
    geom_bar(stat = "identity") + geom_text(aes(label = Set_size, x =  loc_val(mean_FC,SD) ),size = 2.5) +
    geom_linerange(aes(xmin=ifelse(mean_FC < 0,mean_FC - SD, mean_FC), xmax=ifelse(mean_FC > 0,mean_FC + SD, mean_FC) ))
  
  return(p)
}

raw_data <- "/workspaces/phd_dissertation/PIPE/analysis/data/raw_data/"
first <- read.xlsx(paste0(raw_data,"231203_raw_data.xlsx"),sheet = 1)
```

# Mono-culture

## Endothelial 21% O2. Normal shear stress

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_E21_BR|raw_DEN21_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_E21")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
write.csv(x = resLFC[order(resLFC$padj),],file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/degs_E21vsDES21.csv")
```


### Volcano plot

```{r}
p <- volcano_plot(exp = resLFC,down_color = "#a6cee3",up_color = "#1f78b4", title="Static vs Dynamic flow", subtitle="hPMEC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/volcano_E21vsDEN21.pdf",plot=p,device="pdf",units="mm",dpi=600,width = 70,height = 70)
p
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
q <- enrichment_profile(pathways = exp1.reac[1:9,],DEG = degs,
                   color_down = "#a6cee3",color_up = "#1f78b4",title="Static vs Dynamic flow", subtitle="hPMEC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/reactome_E21vsDEN21.pdf",plot=q,device="pdf",units="mm",dpi=600,width = 105,height = 70)
write.csv(x = exp1.reac,file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/reactome_E21vsDES21.csv")
q
```

## Endothelial 21% O2. High shear stress

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_E21_BR|raw_DEH21_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_E21")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

#### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial 40% O2. Normal shear stress

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_E40_BR|raw_DEN40_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_E40")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac,DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial 40% O2. High shear stress

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_E40_BR|raw_DEH40_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_E40")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac,DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

# Co-culture

## Endothelial/smooth muscle 21% O2. Normal shear stress. Endothelial

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES21_E_BR|raw_DESN21_E_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES21_E")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
write.csv(x = resLFC[order(resLFC$padj),],file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/degs_ES21vsDESN21_E.csv")
```

### Volcano plot

```{r}
p <- volcano_plot(exp = resLFC,down_color = "#a6cee3",up_color = "#1f78b4", title="Static vs Dynamic flow", subtitle="hPMEC + hPASMC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/volcano_ES21vsDESN21_E.pdf",plot=p,device="pdf",units="mm",dpi=600,width = 70,height = 70)
p
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
q <- enrichment_profile(pathways = exp1.reac[1:10,],DEG = degs,
                   color_down = "#a6cee3",color_up = "#1f78b4",title="Static vs Dynamic flow", subtitle="hPMEC + hPASMC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/reactome_ES21vsDESN21_E.pdf",plot=q,device="pdf",units="mm",dpi=600,width = 105,height = 70)
write.csv(x = exp1.reac,file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/reactome_ES21vsDESN21_E.csv")
q
```

## Endothelial/smooth muscle 21% O2. Normal shear stress. Smoonth muscle

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES21_S_BR|raw_DESN21_S_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES21_S")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
write.csv(x = resLFC[order(resLFC$padj),],file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/degs_ES21vsDESN21_S.csv")
```

### Volcano plot

```{r}
p <- volcano_plot(exp = resLFC,down_color = "#b2df8a",up_color = "#33a02c", title="Static vs Dynamic flow", subtitle="hPMEC + hPASMC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/volcano_ES21vsDESN21_S.pdf",plot=p,device="pdf",units="mm",dpi=600,width = 70,height = 70)
p
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
q <- enrichment_profile(pathways = exp1.reac[1:10,],DEG = degs,
                   color_down = "#b2df8a",color_up = "#33a02c",title="Static vs Dynamic flow", subtitle="hPMEC + hPASMC")
ggsave("/workspaces/phd_dissertation/PIPE/analysis/figures/static/reactome_ES21vsDESN21_S.pdf",plot=q,device="pdf",units="mm",dpi=600,width = 105,height = 70)
write.csv(x = exp1.reac,file = "/workspaces/phd_dissertation/PIPE/analysis/data/derived_data/reactome_ES21vsDESN21_S.csv")
q
```

## Endothelial/smooth muscle 21% O2. High shear stress. Endothelial

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES21_E_BR|raw_DESH21_E_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES21_E")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial/smooth muscle 21% O2. High shear stress. Smooth muscle

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES21_S_BR|raw_DESH21_S_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES21_S")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial/smooth muscle 40% O2. Normal shear stress. Endothelial

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES40_E_BR|raw_DESN40_E_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES40_E")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```


## Endothelial/smooth muscle 40% O2. Normal shear stress. Smooth muscle

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES40_S_BR|raw_DESN40_S_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES40_S")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

#### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial/smooth muscle 40% O2. High shear stress. Endothelial

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES40_E_BR|raw_DESH40_E_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES40_E")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

## Endothelial/smooth muscle 40% O2. High shear stress. Smooth muscle

```{r}
#| warning: false

counts <- first[,grep(pattern = 'raw_ES40_S_BR|raw_DESH40_S_BR',x = colnames(first))]
rownames(counts) <- first$id

meta <- data.frame(experiment = as.factor(gsub(pattern = "\\_BR[1-3]",replacement = "",x = colnames(counts))))
rownames(meta) <- colnames(counts)

dds <- DESeqDataSetFromMatrix(countData = counts,
                              colData = meta,
                              design = ~experiment)

keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds$experiment <- relevel(dds$experiment, ref = "raw_ES40_S")
dds <- DESeq(dds)
resultsNames(dds)
resLFC <- lfcShrink(dds, coef=2, type="apeglm")
resLFC <- as.data.frame(resLFC) %>% mutate(name = first$name[which(first$id %in% rownames(resLFC))], .before=1)

cat("number of significant genes: ",nrow(resLFC[which(resLFC$padj < 0.05),]))
head(resLFC[order(resLFC$padj),])
```

### Volcano plot

```{r}
volcano_plot(exp = resLFC,down_color = "#FDE725FF",up_color = "#4AC16DFF", title="Endothelial oxygen")
```

### REACTOME

```{r}
#| warning: false

degs <- resLFC[which(resLFC$padj < 0.05),]

exp1.enr <- gost(rownames(degs),organism = "hsapiens",sources=c("REAC"),
                 user_threshold = 0.05)
exp1.reac <- exp1.enr$result[exp1.enr$result$source == "REAC",c("term_id", "source", "term_name", "p_value", "query_size", "term_size", "intersection_size")]
nrow(exp1.reac)
enrichment_profile(pathways = exp1.reac[1:5,],DEG = degs,
                   color_down = "#365C8DFF",color_up = "#440154FF",category = "Reactome Pathways")
```

# Session info

```{r}
sessionInfo()
```